Convective dynamics with mixed temperature boundary conditions: \\ why thermal relaxation matters and how to accelerate it

### 2020-05-20 tex/mixedft_evolution_ms.tex
minor fig caption updates

\begin{figure}[t!]
\includegraphics[width=\textwidth]{./figs/rbc_scalar_comparisons.pdf}
\caption{ 
	(Left three panels) Time traces of scalar quantities in a \ea{classic-IC} FT (orange\ea{, Ra$_{\partial_z T} = 4.81 \times 10^{10}$}) and TT (purple\ea{, Ra$_{\Delta T} = 10^9$}) simulation are shown.
	All traces have been averaged over a rolling window of 100 freefall time units to increase the clarity of the evolutionary trend.
	We display evolutionary traces of Ra (top, normalized by Ra$_{\Delta T}$ of the TT simulation) as well as Nu (middle) and Pe (bottom), both of which are normalized by their mean values measured over the last 500 freefall times of the TT simulation (reported in appendix \ref{app:table}).
	(Right two panels) Compensated scaling plots of Nu (upper) and Pe (lower) vs. Ra$_{\Delta T}$.
	Nu vs.~Ra is compensated by $(0.138 \text{Ra}_{\Delta T}^{0.285})$, the best-fit reported by ref.~\cite{johnston&doering2009}.
	Pe vs.~Ra is compensated by a Ra$_{\Delta T}^{1/2}$ law, the anticipated scaling of Pe \cite{ahlers&all2009}.
	The orange trace is the time evolution of the FT case from the left panels with the arrows showing the sense of time.
	The yellow trace shows the evolution of an FT case with Ra$_{\Delta T} = 10^8$.
	Purple circles are the measured values of Nu and Pe in our TT simulations (reported in appendix \ref{app:table}); error bars show the standard deviation of the sample mean and are smaller than the marker in all cases.
	The purple circles filled in with yellow and orange are the TT comparisons for the evolved states of the two FT cases.
	Black crosses show comparison TT simulations as reported by ref.~\cite{zhu&all2018}.
\label{fig:rbc_scalar_comparisons} }
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{./figs/rbc_dynamics_asymmetries.pdf}
\caption{ 
	(Left panel) PDFs of temperature measurements of a TT-to-FT (orange) and TT (purple) case with Ra$_{\Delta T} = 10^{10}$ are displayed.
	The right tail of the distribution (near the hot fixed-flux boundary for the FT case) shows that fixed flux boundaries achieve more extreme temperature events than fixed temperature boundaries.
	(Middle panel) A snapshot of the temperature anomaly in the FT simulation.
	Zoomed in views of the regions outlined in black boxes are shown in the right two panels.
	Near the top (fixed temperature) boundary, the temperature anomaly at the root of the plume vanishes, but this does not happen near the bottom (fixed flux) boundary, allowing for more extreme instantaneous values.
\label{fig:rbc_dynamics_asymmetries} }
\end{figure}

@@

\begin{figure}[t!]
\includegraphics[width=\textwidth]{./figs/rotating_panels.pdf}
\caption{ 
	(Left three panels) Time traces of scalar quantities in a \ea{classic-IC} FT (orange) and TT (purple) simulation are shown.
	All traces have been averaged over a rolling window of 50 freefall time units to increase the clarity of the evolutionary trend.
	(Top panel) Ra, normalized by the input Ra$_{\Delta T}$ = 2.75$\,\times 10^9$ of the TT simulation.
	(Middle panel) Ro evolution of both simulations; the bulk flow of the FT simulation transitions from a marginally rotationally unconstrained state to a constrained state, while the TT simulation is always rotationally constrained.
	(Bottom panel) Pe evolution of the simulations is shown, normalized by the mean value measured over the last 500 freefall times of the TT simulation.
	(Upper right panel) Parameter space of Nu vs.~Ra$_{\Delta T}$ in rotating convection.
	Circular and diamond data points are respectively simulations and experimental data points from ref.~\cite{cheng&all2015}.
	The color of the data points signifies the Ekman number of the points, and grey diamonds are non-rotating.
	Data from our Ek$\,=\,10^{-6}$ FT experiment are shown as a thick orange line with a cyan interior, where the black arrows give the direction of time.
	Some TT simulations are shown as purple circles with a cyan interior, and the TT case which corresponds to the relaxed state of the FT simulation is shown as a star.
	(Bottom right panels) Snapshots of the vertically integrated z-component of the vorticity from the FT simulation.
	At early times (left panel), a powerful large scale vortex with positive vorticity develops.
	This vortex slowly decays and becomes a vortex pair (middle panel), as seen in ref.~\cite{stellmach&all2014}.
	In the converged state, we see oscillatory behavior between this vortex pair behavior and jets (right panel).
	The TT case exhibits the oscillatory behavior between vortex pairs and jets throughout its whole evolution.
	The three vertical black lines in the left panels signify the times at which these snapshots are taken.
\label{fig:rotating_panels} }
\end{figure}

>>>>

\begin{figure}[t!]
\includegraphics[width=\textwidth]{./figs/rbc_scalar_comparisons.pdf}
\caption{ 
	(Left three panels) Time traces of scalar quantities in a \ea{classic-IC} FT (orange\ea{, Ra$_{\partial_z T} = 4.81 \times 10^{10}$}) and TT (purple\ea{, Ra$_{\Delta T} = 10^9$}) simulation are shown.
	All traces have been averaged over a rolling window of 100 freefall time units to increase the clarity of the evolutionary trend.
	We display evolutionary traces of Ra (top, normalized by Ra$_{\Delta T}$ of the TT simulation) as well as Nu (middle) and Pe (bottom), both of which are normalized by their mean values measured over the last 500 freefall times of the TT simulation (reported in appendix \ref{app:table}).
	(Right two panels) Compensated scaling plots of Nu (upper) and Pe (lower) vs. Ra$_{\Delta T}$.
	Nu vs.~Ra is compensated by $(0.138 \text{Ra}_{\Delta T}^{0.285})$, the best-fit reported by ref.~\cite{johnston&doering2009}.
	Pe vs.~Ra is compensated by a Ra$_{\Delta T}^{1/2}$ law, the anticipated scaling of Pe \cite{ahlers&all2009}.
	The orange trace is the time evolution of the FT case from the left panels with the arrows showing the sense of time.
	The yellow trace shows the evolution of an FT case with Ra$_{\partial_z T} = 2.61 \times 10^9$.
	Purple circles are the measured values of Nu and Pe in our TT simulations (reported in appendix \ref{app:table}); error bars show the standard deviation of the sample mean and are smaller than the marker in all cases.
	The purple circles filled in with yellow and orange are the TT comparisons for the evolved states of the two FT cases.
	Black crosses show comparison TT simulations as reported by ref.~\cite{zhu&all2018}.
\label{fig:rbc_scalar_comparisons} }
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{./figs/rbc_dynamics_asymmetries.pdf}
\caption{ 
	(Left panel) PDFs of temperature measurements of a TT-to-FT (orange, Ra$_{\partial_z T} = 9.51 \times 10^{11}$) and TT (purple, Ra$_{\Delta T} = 10^{10}$) simulation are displayed.
	The right tail of the distribution (near the hot fixed-flux boundary for the FT case) shows that fixed flux boundaries achieve more extreme temperature events than fixed temperature boundaries.
	(Middle panel) A snapshot of the temperature anomaly in the FT simulation.
	Zoomed in views of the regions outlined in black boxes are shown in the right two panels.
	Near the top (fixed temperature) boundary, the temperature anomaly at the root of the plume vanishes, but this does not happen near the bottom (fixed flux) boundary, allowing for more extreme instantaneous values.
\label{fig:rbc_dynamics_asymmetries} }
\end{figure}

@@

\begin{figure}[t!]
\includegraphics[width=\textwidth]{./figs/rotating_panels.pdf}
\caption{ 
	(Left three panels) Time traces of scalar quantities in a \ea{classic-IC} FT (orange, $\text{Ra}_{\partial_z T} = 2.1 \times 10^{10}$) and TT (purple, Ra$_{\Delta T} = 2.75\times 10^9$) simulation are shown.
	All traces have been averaged over a rolling window of 50 freefall time units to increase the clarity of the evolutionary trend.
	(Top panel) Ra, normalized by the input Ra$_{\Delta T}$ of the TT simulation.
	(Middle panel) Ro evolution of both simulations; the bulk flow of the FT simulation transitions from a marginally rotationally unconstrained state to a constrained state, while the TT simulation is always rotationally constrained.
	(Bottom panel) Pe evolution of the simulations is shown, normalized by the mean value measured over the last 500 freefall times of the TT simulation.
	(Upper right panel) Parameter space of Nu vs.~Ra$_{\Delta T}$ in rotating convection.
	Circular and diamond data points are respectively simulations and experimental data points from ref.~\cite{cheng&all2015}.
	The color of the data points signifies the Ekman number of the points, and grey diamonds are non-rotating.
	Data from our Ek$\,=\,10^{-6}$ FT experiment are shown as a thick orange line with a cyan interior, where the black arrows give the direction of time.
	Some TT simulations are shown as purple circles with a cyan interior, and the TT case which corresponds to the relaxed state of the FT simulation is shown as a star.
	(Bottom right panels) Snapshots of the vertically integrated z-component of the vorticity from the FT simulation.
	At early times (left panel), a powerful large scale vortex with positive vorticity develops.
	This vortex slowly decays and becomes a vortex pair (middle panel), as seen in ref.~\cite{stellmach&all2014}.
	In the converged state, we see oscillatory behavior between this vortex pair behavior and jets (right panel).
	The TT case exhibits the oscillatory behavior between vortex pairs and jets throughout its whole evolution.
	The three vertical black lines in the left panels signify the times at which these snapshots are taken.
\label{fig:rotating_panels} }
\end{figure}
